---
title: "Demo-Report-RStudio"
author: "Thang Pham"
date: "5/21/2020"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}

library(tidyverse)
#read csv file into a table called students
students <- read_csv('find-all-students-2020-05-20T21-47-47-982Z.csv')

#delete the id column
students$id <- NULL

#convert the gende column to factor
students$Gender <- factor(students$Gender, labels = c('M', 'F'))

#prduce some summary stats
summary <- students %>%
  summarise(Total_Docs = sum(`Number of Owned Documents`), 
            Total_Comments = sum(`Number of Comments`)) %>%
  mutate(Comment_Doc_Ratio=Total_Comments/Total_Docs)

summary$Total_Docs
summary$Total_Comments
ratio <- round(summary$Comment_Doc_Ratio, 2)

summary2 <- students %>%
  group_by(Courses) %>%
  summarize(Total_Docs = sum(`Number of Owned Documents`), 
                 Total_Comments = sum(`Number of Comments`)) %>%
  mutate(ratio=Total_Comments/Total_Docs) %>%
  arrange(ratio)
  

```

# Comparison of Document Counts and Comment Counts Across 3 Courses

## Data

The data was extracted from a sample database of student users. In total, there are `r summary$Total_Docs` documents and `r summary$Total_Comments` comments authored by all students, with an average document:comment ratio of `r ratio`.  

```{r overview, echo=FALSE}
students %>%
  group_by(Courses) %>%
  summarise(Total_Docs = sum(`Number of Owned Documents`), 
            Total_Comments = sum(`Number of Comments`)) %>%
  gather(Total_Docs, Total_Comments, key='Total', value='value') %>%
  arrange(Courses) %>%
  ggplot(aes(x=Total, y=value, fill=Courses)) +
  geom_col(position = 'dodge') +
  xlab('') +
  ylab('Count') +
  ggtitle('Document Counts vs Comment Counts By Courses')
```

While it is not surprising that there are more comments than documents, effective online learning seems to generate by far the highest level of productivity, with a comment/doc ratio of `r summary2$ratio[3]`, about `r round(summary2$ratio[3]/mean(c(summary2$ratio[1], summary2$ratio[2])), 0)` times higher than the other two courses. 

```{r doc/comment ratio, echo=FALSE}
summary2 %>%
  ggplot(aes(x=Courses, y=ratio, fill=Courses)) +
  geom_col() +
  ggtitle('Comment/Document Ratio Across 3 Courses')
```

## Implications

The two charts and above analyses suggest that there is room to improve the interactivity of the 2 courses Ocean Browser and Studio Project 1. 

Further research should be carried out to investigate what makes Effectie Online Learning so engaging.